A Catalogue of Twists of Supersymmetric Gauge Theories

### 2020-01-23 paper.tex
List of twists in intro

\textbf{Dimension 8}
\begin{itemize}
 \item \emph{$\mc N=1$ holomorphic twist.} 
 \item \emph{$\mc N=1$ intermediate twist.}
 \item \emph{$\mc N=1$ topological twist.} \cite{AcharyaOLoughlinSpence,BaulieuKannoSinger}
\end{itemize}

\textbf{Dimension 7}
\begin{itemize}
 \item \emph{$\mc N=1$ minimal twist.} 
 \item \emph{$\mc N=1$ intermediate twist.}
 \item \emph{$\mc N=1$ topological twist.} 
\end{itemize}

\textbf{Dimension 6}
\begin{itemize}
 \item \emph{$\mc N=(1,0)$ and $\mc N=(1,1)$ holomorphic twist.} 
 \item \emph{$\mc N=(1,1)$ special rank $(1,1)$ twist.}
 \item \emph{$\mc N=(1,1)$ rank $(2,2)$ twist.}
 \item \emph{$\mc N=(1,1)$ topological twist.} 
\end{itemize}

>>>>

\textbf{Dimension 8}
\begin{itemize}
 \item \emph{$\mc N=1$ holomorphic twist.} Super Yang-Mills theory in 8 dimensions admits three classes of twist.  The minimal twist, by a holomorphic supercharge, is equivalent to a holomorphic version of BF theory.  This theory is $\mr U(4)$-invariant, and can be defined on arbitrary complex 4-folds.
 \item \emph{$\mc N=1$ intermediate twist.} This minimal twist admits a further twist which is topological in two directions and holomorphic in the remaining three complex directions.  This intermediate twisted theory is equivalent, as a $\ZZ/2\ZZ$-graded theory, to a mixed version of Chern-Simons theory.  It is $\SU(3) \times \Spin(2;\RR)$-invariant, and can be defined on the product of a Calabi-Yau 3-fold and a Riemann surface.
 \item \emph{$\mc N=1$ topological twist.}  There is, finally, a novel topological twist in 8-dimensions, which does not arise via dimensional reduction from the theories above.  This theory is perturbatively trivial, in the sense that the classical BV complex is contractible.  It can, however, be realised as the generic point in a 1-parameter degeneration of the holomorphic twist.  This theory is $\spin(7;\RR)$-invariant, although the full one-parameter family is only $\SU(4)$-invariant.  This theory was studied in \cite{AcharyaOLoughlinSpence,BaulieuKannoSinger}; its equations of motion include the $\spin(7)$-instanton equation.
\end{itemize}

\textbf{Dimension 7}
\begin{itemize}
 \item \emph{$\mc N=1$ minimal twist.} The twists of super Yang-Mills theory in 7 dimensions arise by dimensionally reducing the twists in 8 dimensions.  The minimal twist is equivalent to a mixed version of BF theory with one topological direction and three complex holomorphic directions.  This theory is $\mr U(3)$-invariant, and can be defined on the product of a complex 3-fold with a flat 1-manifold.
 \item \emph{$\mc N=1$ intermediate twist.} This minimal twist admits a further twist which is topological in three directions and holomorphic in the remaining two complex directions.  This intermediate twisted theory is equivalent, as a $\ZZ/2\ZZ$-graded theory, to a mixed version of Chern-Simons theory.  It is $\SU(2) \times \Spin(3;\RR)$-invariant, and can be defined on the product of a Calabi-Yau surface and a 3-manifold with spin structure.
 \item \emph{$\mc N=1$ topological twist.} The topological twist in 8-dimensions reduces to a topological twist in 7 dimensions.  This theory is again perturbatively trivial, but can be realized as the generic point in a 1-parameter degeneration of the minimal twist.  This theory is $G_2$-invariant, although the full one-parameter family is only $\SU(3)$-invariant.  This theory was also studied in \cite{AcharyaOLoughlinSpence}; its equations of motion include the $G_2$-monopole equations.
\end{itemize}

\textbf{Dimension 6}
\begin{itemize}
 \item \emph{$\mc N=(1,0)$ and $\mc N=(1,1)$ holomorphic twist.} There is a holomorphic twist in 6 dimensions that can be defined for the $\mc N=(1,0)$ supersymmetric theory coupled to a hypermultiplet valued in a symplectic representation $U$.  This twist is equivalent to holomorphic Chern-Simons theory coupled to a holomorphic symplectic boson valued in the representation $U$.  It is generally only $\ZZ/2\ZZ$-graded, but can be promoted to a $\ZZ$-graded theory when $U = T^*R$ is of cotangent type.  It is invariant for the action of $\SU(3)$ in general, and can be defined on Calabi-Yau 3-folds, and $\mr U(3)$ in the cotangent case, and can be defined on arbitrary complex 3-folds.  When $U = T^*\gg$, the supersymmetry can be promoted to $\mc N=(1,1)$ supersymmetry, and the twist can be identified with a holomorphic BF theory coupled to adjoint holomorphic matter \chris{something was studied by \cite{BaulieuBossard} in the pure $\mc N=(1,0)$ case, but it doesn't look the same?}
 \item \emph{$\mc N=(1,1)$ special rank $(1,1)$ twist.}
 \item \emph{$\mc N=(1,1)$ rank $(2,2)$ twist.}
 \item \emph{$\mc N=(1,1)$ topological twist.} 
\end{itemize}
